On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-20 paper/paper.tex
Update title
Next draft of abstract

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\
\large{Not For Distribution}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Domain specific languages (DSLs) provide a powerful tool for abstracting over
  a class of problems. In this paper, we introduce a technique for representing
  algebraic data types and pattern matching in a DSL embedded in Haskell. This
  representation is mechanized through the use of GHC Generics and a GHC Core plugin.
\end{abstract}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{On Adding Pattern Matching to Haskell-based
  Deeply Embedded Domain Specific Languages\\
\large{Not For Distribution}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  %Say what problem is
  The data flow in deeply embedded domain specific langauges  falls out naturally.

  Capturing control flow in embbed
  is critical for 
  Using a deep embedding of 
 Programs that write programs 
  Sometimes,  
Embedded Domain Specific Languages are the killer app of functional languages.
%Say why it is an interesting problem
Languages with reification of code fragments allows
for high-level abstractions that directly support
diverse applications incuding machine learning and hardware description generation.
% 
  Haskell in particual has been used for many embeded code generators, such
as Lava, SunRoof, Conal work, CCC, AD, ... (finally tagless) diagrams?
%Say what our solution achieves
In this paper, we expand the capabilies of traditional,
Haskell-based, deep embeddings with a compiler extension
for capturing the useful abstraction of pattern matching. 
%Here is why the world will be a better place
With this new support, the Haskell that we capture for expressing
embededed-based solutions can be cleaner, more Haskell idiomatic,
and more declaritive in nature.

  Domain specific languages (DSLs) provide a powerful tool for abstracting over
  a class of problems.
  This
  representation is mechanized through the use of GHC Generics and a GHC Core plugin.
\end{abstract}
